---
title: "Seasonal/Annual Surface Temperatures (GrIS)"
author: "Shayne O'Brien"
date: "January 28, 2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
The object of this item is to create Tables and Time Series for each year and each season for the PROMICE AWSs between 2009 and 2018.

```{r,message=FALSE, error=FALSE}
library(tidyr)
library(dplyr)
library(ggplot2)
```

#K - Transect

#Read in Data
```{r}
kan_u_df <- read.table(header = T, "Kan_U_day.txt", stringsAsFactors=FALSE) %>% 
  subset(AirTemperature.C. != -999)
kan_m_df <- read.table(header = T, "Kan_M_day.txt")
kan_l_df <- read.table(header = T, "Kan_L_day2.txt")

#head(kan_u_df)
```
##Create Target Table

Create a table for only Year, Month, Day, Air temperature.

Then, add a new binary column, 1 for >0C, 0 for <0C

```{r}

KAN_U <- kan_u_df %>% 
  select(Year, MonthOfYear, AirTemperature.C) %>% 
  KAN_U$Melt <- as.numeric(KAN_U$AirTemperature.C. > 0)
  
  

KAN_M <- kan_m_df %>% 
  select(Year, MonthOfYear, DayOfMonth, AirTemperature.C.)
  KAN_M$Melt <- as.numeric(KAN_M$AirTemperature.C. > 0)

KAN_L <- kan_l_df %>% 
  select(Year, MonthOfYear, DayOfMonth, AirTemperature.C.)  
  KAN_L$Melt <- as.numeric(KAN_L$AirTemperature.C. > 0)
  
head(KAN_U)
  

```
##Aggragate columns
```{r}

```




##Isolate Temperatures by Year

##Isolate Temperatures by Season

##Plot
```{r}
kan_u_plot <- kan_u_df
kan_u_plot$Date <- as.Date(with(kan_u_plot, paste(Year, MonthOfYear, DayOfMonth,sep="-")), "%d-%m-%Y")
   
   
ggplot(kan_u_plot, aes(DayOfCentury, AirTemperature.C.))+
  geom_line()

  
  

```

