---
title: "Seasonal/Annual Surface Temperatures (GrIS)"
author: "Shayne O'Brien"
date: "January 28, 2019"
output:
  html_document:
    toc: true
    toc_float: true
    theme: united
    toc_depth: 3
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
#Objective
The object of this item is to create Tables and Time Series for each year and each season for the PROMICE AWSs between 2009 and 2018.

The following packages are needed to reproduce these results

```{r,message=FALSE, error=FALSE, echo = FALSE}
library(tidyr)
library(dplyr)
library(ggplot2)
library(DT)
library(leaflet)
```
#Interactive Map
Mouse over the markers to locate each station examined in the study
```{r}
locations <- read.csv(header = T, "PROMICE Stations.csv")

leaflet(locations) %>% 
  addTiles() %>% 
  addMarkers(~ Long, ~ Lat, popup = ~Station_Name)

```


#K - Transect

```{r, echo = FALSE}
kan_u_df <- read.table(header = T, "Kan_U_day.txt") %>% 
  subset(AirTemperature.C. != -999)
kan_m_df <- read.table(header = T, "Kan_M_day.txt") %>% 
  subset(AirTemperature.C. != -999)
kan_l_df <- read.table(header = T, "Kan_L_day2.txt") %>% 
  subset(AirTemperature.C. != -999)

```

```{r, echo = FALSE}
##Create Target Table

#Create a table for only Year, Month, Day, Air temperature.

#Then, add a new binary column, 1 for >0C, 0 for <0C

KAN_U <- kan_u_df %>% 
  select(Year, MonthOfYear, AirTemperature.C.) 
  KAN_U$Melt <- as.numeric(KAN_U$AirTemperature.C. > 0)
  
KAN_M <- kan_m_df %>% 
  select(Year, MonthOfYear, DayOfMonth, AirTemperature.C.)
  KAN_M$Melt <- as.numeric(KAN_M$AirTemperature.C. > 0)

KAN_L <- kan_l_df %>% 
  select(Year, MonthOfYear, DayOfMonth, AirTemperature.C.)  
  KAN_L$Melt <- as.numeric(KAN_L$AirTemperature.C. > 0)
  
#head(KAN_U)
  

```
##Monthly and Annual Tables

###KAN U  
```{r, echo=FALSE}
kan_u_season <- KAN_U %>%
  rename(Month = MonthOfYear) %>% 
  mutate(Year = as.numeric(Year)) %>%
  group_by(Year, Month) %>%
  summarise(MeltDays = sum(Melt)) %>% 
  spread(Month, MeltDays)

kan_u_annual <- KAN_U %>%
  select(Year, Melt) %>% 
  mutate(Year = as.numeric(Year)) %>%
  group_by(Year) %>%
  summarise(MeltDays = sum(Melt))
  
datatable(
  kan_u_season, class = 'cell-border stripe', 
  rownames = FALSE, 
  colnames = c('Jan', 'Feb','Mar', 'Apr', 'May', 'Jun', 'July', 'Aug', 'Sep', 'Oct', 'Nov', 'Dec'),
  caption = htmltools::tags$caption(
  style = 'caption-side: bottom; text-align: center,',
  'Table 1: ', htmltools::em('This table displays the number of days per month with a temperature of > 0deg Celsius, 2009-2018')
  ))
datatable(
  kan_u_annual, class = 'cell-border stripe', 
  rownames = FALSE,
  caption = htmltools::tags$caption(
  style = 'caption-side: bottom; text-align: center,',
  'Table 1: ', htmltools::em('This table displays the number of days annually with a temperature of > 0deg Celsius, 2009-2018')
  ))

##c(Melt,Year(2009)))summarise(KAN_U, sum = sum(Melt))
#summarise(KAN_U, "2009" = sum(
```
### KAN M  

```{r, echo = FALSE}
kan_m_season <- KAN_M %>%
  rename(Month = MonthOfYear) %>% 
  mutate(Year = as.numeric(Year)) %>%
  group_by(Year, Month) %>%
  summarise(MeltDays = sum(Melt)) %>% 
  spread(Month, MeltDays)

kan_m_annual <- KAN_M %>%
  select(Year, Melt) %>% 
  mutate(Year = as.numeric(Year)) %>%
  group_by(Year) %>%
  summarise(MeltDays = sum(Melt))
  
datatable(
  kan_m_season, class = 'cell-border stripe', 
  rownames = FALSE, 
  colnames = c('Jan', 'Feb','Mar', 'Apr', 'May', 'Jun', 'July', 'Aug', 'Sep', 'Oct', 'Nov', 'Dec'),
  caption = htmltools::tags$caption(
  style = 'caption-side: bottom; text-align: center,',
  'Table 1: ', htmltools::em('This table displays the number of days per month with a temperature of > 0deg Celsius, 2009-2018')
  ))
datatable(
  kan_m_annual, class = 'cell-border stripe', 
  rownames = FALSE,
  caption = htmltools::tags$caption(
  style = 'caption-side: bottom; text-align: center,',
  'Table 1: ', htmltools::em('This table displays the number of days annually with a temperature of > 0deg Celsius, 2009-2018')
  ))
```
### KAN L  

```{r, echo=FALSE}
kan_l_season <- KAN_L %>%
  rename(Month = MonthOfYear) %>% 
  mutate(Year = as.numeric(Year)) %>%
  group_by(Year, Month) %>%
  summarise(MeltDays = sum(Melt)) %>% 
  spread(Month, MeltDays)

kan_l_annual <- KAN_L %>%
  select(Year, Melt) %>% 
  mutate(Year = as.numeric(Year)) %>%
  group_by(Year) %>%
  summarise(MeltDays = sum(Melt))
  
datatable(
  kan_l_season, class = 'cell-border stripe', 
  rownames = FALSE, 
  colnames = c('Jan', 'Feb','Mar', 'Apr', 'May', 'Jun', 'July', 'Aug', 'Sep', 'Oct', 'Nov', 'Dec'),
  caption = htmltools::tags$caption(
  style = 'caption-side: bottom; text-align: center,',
  'Table 1: ', htmltools::em('This table displays the number of days per month with a temperature of > 0deg Celsius, 2009-2018')
  ))
datatable(
  kan_l_annual, class = 'cell-border stripe', 
  rownames = FALSE,
  caption = htmltools::tags$caption(
  style = 'caption-side: bottom; text-align: center,',
  'Table 1: ', htmltools::em('This table displays the number of days annually with a temperature of > 0deg Celsius, 2009-2018')
  ))
```

## Surface Temperature Timeseries

### KAN U   

```{r fig.height=10, fig.width=12, echo = FALSE}
kan_u_plot <- kan_u_df
kan_u_plot$Date <- as.Date(with(kan_u_plot, paste(Year, MonthOfYear, DayOfMonth,sep="-")), "%d-%m-%Y")
   
   
ggplot(kan_u_plot, aes(DayOfYear, AirTemperature.C.))+
  geom_line()+
  facet_wrap(~Year,scales = "fixed", ncol = 2)+
  xlab("Degrees C")+
  ylab("Day of Year")
  
  

  
  

```

### KAN M  

```{r fig.height=10, fig.width=12, echo = FALSE}
kan_m_plot <- kan_m_df
#kan_m_plot$Date <- as.Date(with(kan_m_plot, paste(Year, MonthOfYear, DayOfMonth,sep="-")), "%d-%m-%Y")
   
   
ggplot(kan_m_plot, aes(DayOfYear, AirTemperature.C.))+
  geom_line()+
  facet_wrap(~Year,scales = "fixed", ncol = 2)+
  xlab("Degrees C")+
  ylab("Day of Year")
  
  

```

### KAN L  

```{r fig.height=10, fig.width=12, echo = FALSE}
kan_l_plot <- kan_l_df
#kan_l_plot$Date <- as.Date(with(kan_u_plot, paste(Year, MonthOfYear, DayOfMonth,sep="-")), "%d-%m-%Y")
   
   
ggplot(kan_l_plot, aes(DayOfYear, AirTemperature.C.))+
  geom_line()+
  facet_wrap(~Year,scales = "fixed", ncol = 2)+
  xlab("Degrees C")+
  ylab("Day of Year")
  

```

