---
title: "RadiativeFlux"
author: "Shayne O'Brien"
date: "February 22, 2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
#Objective
  The objective of this study is to extract radiative flux numbers to compare to other phenomena.
```{r,message=FALSE, error=FALSE, echo = FALSE}
library(tidyr)
library(dplyr)
library(ggplot2)
library(DT)
library(leaflet)
```

```{r, echo = FALSE}
kan_u_df <- read.table(header = T, "Kan_U_day.txt") %>% 
  subset(AirTemperature.C. != -999)
kan_m_df <- read.table(header = T, "Kan_M_day.txt") %>% 
  subset(AirTemperature.C. != -999)
kan_l_df <- read.table(header = T, "Kan_L_day2.txt") %>% 
  subset(AirTemperature.C. != -999)
```

```{r, echo = FALSE}
##Create Target Table
#Create a table for only Year, Month, Day, Air temperature.
#Then, add a new binary column, 1 for >0C, 0 for <0C
KAN_U <- kan_u_df %>% 
  select(Year, MonthOfYear, LongwaveRadiationDown.W.m2., LongwaveRadiationUp.W.m2., ShortwaveRadiationDown.W.m2., ShortwaveRadiationUp.W.m2.) 
  KAN_U$NetLW <- as.numeric(KAN_U$LongwaveRadiationDown.W.m2. - KAN_U$LongwaveRadiationUp.W.m2.)
  KAN_U$NetSW <- as.numeric(KAN_U$ShortwaveRadiationDown.W.m2. - KAN_U$ShortwaveRadiationUp.W.m2.)
  head(KAN_U)
  
KAN_M <- kan_m_df %>% 
  select(Year, MonthOfYear, LongwaveRadiationDown.W.m2., LongwaveRadiationUp.W.m2., ShortwaveRadiationDown.W.m2., ShortwaveRadiationUp.W.m2.) 
  KAN_M$NetLW <- as.numeric(KAN_M$LongwaveRadiationDown.W.m2. - KAN_M$LongwaveRadiationUp.W.m2.)
  KAN_M$NetSW <- as.numeric(KAN_M$ShortwaveRadiationDown.W.m2. - KAN_M$ShortwaveRadiationUp.W.m2.)

KAN_U <- kan_u_df %>% 
  select(Year, MonthOfYear, LongwaveRadiationDown.W.m2., LongwaveRadiationUp.W.m2., ShortwaveRadiationDown.W.m2., ShortwaveRadiationUp.W.m2.) 
  KAN_U$NetLW <- as.numeric(KAN_U$LongwaveRadiationDown.W.m2. - KAN_U$LongwaveRadiationUp.W.m2.)
  KAN_U$NetSW <- as.numeric(KAN_U$ShortwaveRadiationDown.W.m2. - KAN_U$ShortwaveRadiationUp.W.m2.)
  
  
```

##Monthly and Annual Tables

###KAN U  
```{r, echo=FALSE}
kan_u_season <- KAN_U %>%
  rename(Month = MonthOfYear) %>% 
  mutate(Year = as.numeric(Year)) %>%
  group_by(Year, Month) %>%
  summarise(MeltDays = sum(Melt)) %>% 
  spread(Month, MeltDays)
kan_u_annual <- KAN_U %>%
  select(Year, Melt) %>% 
  mutate(Year = as.numeric(Year)) %>%
  group_by(Year) %>%
  summarise(MeltDays = sum(Melt))